### 2023-03-24 main.tex
ii

\subsection{Informal description}

@@

\Omega_{x}:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}

@@

This measure has marginals $\mu_{rev}^{x}$ distributed as 

@@

To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{dualityIntertwines} is fulfilled.  To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description. Indeed, in this formalism the proof reduces in finding symmetries and exponential transformation of generators of the Lie algebra.\\

@@

The Hamiltonian of the dual process reads as

@@

The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} with respect to the duality matrix $D$ defined as 

@@

Since \eqref{dualityMatrix} is product over sites, \eqref{DualityRelation} is equivalent to proving that 

@@

We perform the proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}. 

@@

Fix an arbitrary site $x\in V$
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle

@@

\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}||q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}

@@

&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\chi}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&=
\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|_{x}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
\\&\cdot 
\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1},\ldots,r_{N}\rangle_{x}\\&=
\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}

@@

We show that 
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\left(\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|\right)
	\sum_{s^{x}\in \Omega_{x},}\left(s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
	\sum_{n_{x}\in\Omega_{x}}\left(\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|\right)

@@

We now search for a symmetry of $H_{x,y}$. Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
    [A,B]=0
Moreover, since the coproduct is a Lie algebra homomorphism we have that 
\begin{equation}\label{symmetryCoproduct}
    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, we can search for a symmetry of $C_{2}$. $C_{2}$ is a central for $gl(N)$, i.e. it commutes with all the element of the the algebra. We consider 
\begin{equation}\label{equationE}
    E=\sum_{a=2}^{N}E_{a1}
To obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we take the exponential of this matrix, i.e. we introduce the symmetry
    S=\exp{(\Delta(E))}
Since $[C_{2},E]=0$, we have that 
\begin{equation}\label{commutationSC}
    \left[S,\Delta(C_{2})\right]=0
For fixed $(x,y)\in \mathcal{E}$ we introduce
    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{commutationSC}, we have that 
\begin{equation}\label{symmetryH}
    \left[S_{x,y},H_{x,y}\right]=0
i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we obtain that 
        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        DH_{x,y}
 where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
 \newline\newline
 \textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
 {\color{blue} That's confusing. What is E?}

 However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \begin{flushright}
     $\square$
 \end{flushright}
 \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site $\widehat{x}$ that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, we can write the Hadamard formula as 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
 \end{equation}
For the following of the proof we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
\begin{enumerate}
    \item for $A=E_{\ell 1}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{\ell 1}\exp{(E)}=E_{\ell 1}
    \end{equation}
    because $E_{\ell 1}$ commutes with $E$
    \item for $A=E_{\ell\ell}$ with $\ell \in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{\ell \ell}\exp{(E)}=E_{\ell \ell}+E_{\ell 1}
    \end{equation}
Indeed, using \eqref{eq:comgl} we have 
    \begin{equation}
       \left[E, E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{\ell 1}-E_{\ell 1}\delta_{a\ell}\right)=-E_{l1}
    \end{equation}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{1\ell}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{1 \ell}\exp{(E)}=E_{1\ell}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{j\ell}\right)
    \end{equation}
  \com{Why indices have names $\ell, k, j, a, b$? Fix one set for the generators}

@@

where $E^{x}$ is a copy of $E$ acting on site $x\in V$ and $E_{ab}^{x}$ with $a,b\in \{1,\ldots,N\}$ are copies of $E_{ab}$ acting at site $x\in V$. Using \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that 

@@

&H_{x,y}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

     &H_{x,y}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

>>>>

\subsection{Informal description of the process}

@@

\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}^{x}=\twoj\right\}

@@

This measure has marginals $\mu_{rev}^{x}$ given by 

@@

To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{dualityIntertwines} is fulfilled.  To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description. Indeed, in this formalism the proof reduces to finding symmetries and exponential transformation of generators of the Lie algebra.\\

@@

The Hamiltonian of the dual process reads

@@

We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} where the duality matrix $D$ is described as 

@@

Since \eqref{dualityMatrix} is product over sites, proving \eqref{DualityRelation} is equivalent to showing that 

@@

We perform the duality proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}. 
As a preliminary result we show the following property 
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|

@@

Fix an arbitrary site $x\in V$, then we have that 
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|
	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle
where we used \eqref{transpositionPropertyR}. \\

@@

\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}

@@

&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
\hspace{2.cm}\qquad|r_{1}^{x},\ldots,r_{N}^{x}\rangle
\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|
\hspace{2.cm}\prod_{a=2}^{N}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle
\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
\hspace{2.cm}\qquad\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle
\frac{(\nu-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}

@@

@@

As a consequence of \eqref{hamiltonianCasimir} we look for a symmetry of  $\Delta(C_{2})$.

%We now search for a symmetry of $H_{x,y}$. % Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
%\begin{equation}
%    [A,B]=0
%\end{equation}
Since the coproduct is a Lie algebra homomorphism we have that $\forall A,B\in gl(N)$
\begin{equation}\label{symmetryCoproduct}
    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
\end{equation}
%Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, it is enough to identify a symmetry of $C_{2}$. But
 $C_{2}$ is in the center of $gl(N)$, and therefore it commutes with all the element of the the algebra. Considering 
\begin{equation}\label{equationE}
    E=\sum_{a=2}^{N}E_{a1}
\end{equation}
to obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we chose as a symmetry 
\begin{equation}
    S=\exp{(\Delta(E))}
\end{equation}
%Since $[C_{2},E]=0$, we have that 
%\begin{equation}\label{commutationSC}
    %\left[S,\Delta(C_{2})\right]=0
%\end{equation}
For fixed $(x,y)\in \mathcal{E}$ we introduce
\begin{equation}
    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{symmetryCoproduct}, we have that 
\begin{equation}\label{symmetryH}
    \left[S_{x,y},H_{x,y}\right]=0
\end{equation}
i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we obtain that 
\begin{equation}
    \begin{split}
        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=
        DH_{x,y}
    \end{split}
\end{equation}
 where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
 %\textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
 %{\color{blue} That's confusing. What is E?}

% However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \begin{flushright}
     $\square$
 \end{flushright}
 \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $\widehat{x}$. % that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, the Hadamard formula reads 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
 \end{equation}
In the followin we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
\begin{enumerate}
    \item for $A=E_{\ell 1}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{\ell 1}\exp{(E)}=E_{\ell 1}
    \end{equation}
    because $E_{\ell 1}$ commutes with $E$
    \item for $A=E_{\ell\ell}$ with $\ell \in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{\ell \ell}\exp{(E)}=E_{\ell \ell}+E_{\ell 1}
    \end{equation}
Indeed, using \eqref{eq:comgl} we have 
    \begin{equation}
       \left[E, E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{\ell 1}-E_{\ell 1}\delta_{a\ell}\right)=-E_{l1}
    \end{equation}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{1\ell}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{1 \ell}\exp{(E)}=E_{1\ell}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{j\ell}\right)
    \end{equation}
  \com{Why indices have names $\ell, k, j, a, b$? Fix one set for the generators}

@@

%where $E^{x}$ is a copy of $E$ acting on site $x\in V$ and $E_{ab}^{x}$ with $a,b\in \{1,\ldots,N\}$ are copies of $E_{ab}$ acting at site $x\in V$.
 Using \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that 

@@

&H_{x}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

H_{x}^{T}\left(d_{x}\otimes \dd\right)&=
     H_{x}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\widetilde{H}_{x}
\left(d_{x}\otimes \dd\right)\widetilde{H}_{x}
